Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-06-19 analyses/scripts/orv_sys_rev_supplementary.Rmd
Expanded the setup chunk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Sets the working directory for subsequent chunks, but not this chunk
#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      dev = 'png', 
                      out.height = "\\textheight",  
                      out.width = "\\textwidth", 
                      message = FALSE, 
                      warning = FALSE
                      )
```
